Market Expectations and Mangerial Turnover

### 2024-02-24 paper.qmd
some paper updates
update:     git add .     git commit -m "update"     git push

## Manager spell profiles
We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024.  We use 
three sources 1. [league of managers association](https://leaguemanagers.com) a body representing professional managers in English football. 2. [Soccer base](https://www.soccerbase.com) a betting website 3. [Transfermkt website](https://www.transfermarkt.co.uk) a large website which records manager, player and team profiles as well as a large array of analytics of the valuation of playing staff.  The raw data is gathered using a series of web scrapping algorithms. Our primary source of informatoin is Transfermkt, but we use other sources to validate these manager spells.

```{r}
library(readxl)
spells_raw = read_csv("raw_data/club_manager_histories_df.csv")
skimr::skim(spells_raw)

>>>>

## Manager spell profiles

We build a hand-craft database on the complete manager turnover profiles of all professional football managers across 11 European leagues for 23 playing seasons up to 2023-2024. We use three sources 1. [league of managers association](https://leaguemanagers.com) a body representing professional managers in English football. 2. [Soccer base](https://www.soccerbase.com) a betting website 3. [Transfermkt website](https://www.transfermarkt.co.uk) a large website which records manager, player and team profiles as well as a large array of analytics of the valuation of playing staff. The raw data is gathered using a series of web scrapping algorithms. Our primary source of information is Transfermkt, but we use other sources to validate these manager spells.

```{r}
library(readxl)
spells1 = read_csv("raw_data/manager_spells_from_manager_urls_mgronly.csv")
lspells2 = read_csv("raw_data/club_manager_histories_df.csv")
skimr::skim(spells_raw)
```
